---
title: "DHODH analysis - AC16 and IPS"
author: "Pauline Brochet"
date: last-modified # More robust than Sys.Date for frozen files
date-format: long

format:
  html:
    theme: litera
    css: styles.css
    code-fold: true
    toc: true
    toc-expand: true
    toc-depth: 6
    number-sections: true
    embed-resources: true # Makes the HTML portable (optional)
    smooth-scroll: true

execute:
  # Stops re-rendering finished .qmd files unless the source changes
  freeze: auto 
  cache: true
  # General output cleaning
  warning: false
  message: false

editor:
  # Crucial for Positron/VS Code interactivity
  render-on-save: false
  # Forces the preview to open in a pane on the right
  viewer: side 
---


# Prepare working environment

## Config

```{r}
#| cache: false
source("02.Rscripts/library.R")
load_project_libraries()

theme_set(theme_minimal(base_size = 12))
```

```{r}
#| cache: false

source("02.Rscripts/config.R")
source("02.Rscripts/transcriptomic.R")
source("02.Rscripts/proteomic.R")
source("02.Rscripts/metabolomic.R")
source("02.Rscripts/enrichment.R")
source("02.Rscripts/clustering.R")

```

# Transcriptomic

```{r}
#| message = FALSE
#| warning = FALSE

### This chunk lists all input files. ###
```

## AC16

### DEG

```{r}
# AC16 transcriptomics pipeline
# This caller uses the same transcriptomics functions as the iPSC workflow.
# Project-specific comparison definitions are stored in config.R.

# 1. Define output folders.
out_dir_ac16 <- file.path(PATH.AC16_results, "01.Transcriptomic")
deg_dir_ac16 <- file.path(out_dir_ac16, "deg")
dir.create(deg_dir_ac16, recursive = TRUE, showWarnings = FALSE)

# 2. Load AC16 sample metadata.
meta_ac16 <- read_tsv(PATH.TRANSCRIPTOMIC_SAMPLE_METADATA) %>% 
  filter(dataset == TRANSCRIPTOMIC_AC16_DATASET)

# 3. Normalize counts and generate QC plots for AC16.
message("Running normalization for AC16 transcriptomics.")
normalize_and_qc(
  counts_path = PATH.TRANSCRIPTOMIC_RAW_DATA, 
  meta = meta_ac16, 
  dataset = TRANSCRIPTOMIC_AC16_DATASET, 
  out_dir = out_dir_ac16
)

# 4. Run all AC16 DEG comparisons defined in config.R.
for (i in seq_len(nrow(TRANSCRIPTOMIC_AC16_DEG_COMPARISONS))) {
  comparison <- TRANSCRIPTOMIC_AC16_DEG_COMPARISONS[i, ]

  message("Running DEG comparison: ", comparison$tag,
          " [", comparison$section, "]")

  run_deg(
    counts_path = PATH.TRANSCRIPTOMIC_RAW_DATA, 
    meta = meta_ac16, 
    dataset = TRANSCRIPTOMIC_AC16_DATASET, 
    subset_expr = comparison$subset_expr,
    design = comparison$design,
    contrast = c(
      comparison$contrast_factor,
      comparison$contrast_case,
      comparison$contrast_control
    ),
    tag = comparison$tag, 
    out_dir = deg_dir_ac16
  )
}

message("AC16 transcriptomics analysis complete. Results written to: ", out_dir_ac16)
```

### Enrichment analysis

```{r}
# AC16 transcriptomics enrichment
# Run Reactome GSEA and g:Profiler enrichment for every AC16 DEG table
# produced by the previous chunk.

ac16_enrichment_analysis <- TRANSCRIPTOMIC_ENRICHMENT_ANALYSES %>%
  filter(dataset == TRANSCRIPTOMIC_AC16_DATASET)

stopifnot(nrow(ac16_enrichment_analysis) == 1)

message("\nRunning transcriptomics enrichment for: ",
        ac16_enrichment_analysis$dataset)

run_enrichment_for_deg_directory(
  deg_dir = ac16_enrichment_analysis$deg_dir,
  out_dir = ac16_enrichment_analysis$out_dir,
  gene_col = ac16_enrichment_analysis$gene_col,
  fc_col = ac16_enrichment_analysis$fc_col,
  padj_col = ac16_enrichment_analysis$padj_col,
  lfc_cut = ac16_enrichment_analysis$lfc_cut,
  padj_cut = ac16_enrichment_analysis$padj_cut,
  gene_type = ac16_enrichment_analysis$gene_type
)
```


### Mitocarta-specific mapping

```{r}
# AC16 transcriptomics MitoCarta plots
# Generate MitoCarta-specific detailed tables and signed pathway barplots
# from the AC16 transcriptomics DEG tables.

ac16_mitocarta_analysis <- TRANSCRIPTOMIC_MITOCARTA_ANALYSES %>%
  filter(dataset == TRANSCRIPTOMIC_AC16_DATASET)

stopifnot(nrow(ac16_mitocarta_analysis) == 1)

run_mitocarta_plots_transcriptomics(
  deg_dir = ac16_mitocarta_analysis$deg_dir,
  mitocarta_file = ac16_mitocarta_analysis$mitocarta_path,
  out_dir = ac16_mitocarta_analysis$out_dir,
  dataset = ac16_mitocarta_analysis$dataset,
  output_prefix = ac16_mitocarta_analysis$output_prefix,
  contrast_keep = NULL,
  lfc_cut = ac16_mitocarta_analysis$lfc_cut,
  padj_cut = ac16_mitocarta_analysis$padj_cut,
  levels_keep = ac16_mitocarta_analysis$levels_keep
)
```

### Glycolysis/mitocarta volcano plot

```{r}
# AC16 transcriptomics volcano restricted to MitoCarta and KEGG/Reactome
# glycolysis genes, with C/T and C/C shown as side-by-side panels.

plot_mitocarta_glycolysis_volcano(
  comparisons = TRANSCRIPTOMIC_AC16_GLYCO_MITO_VOLCANO$comparisons,
  mitocarta_file = PATH.MITOCARTA_DB,
  out_dir = TRANSCRIPTOMIC_AC16_GLYCO_MITO_VOLCANO$out_dir,
  output_prefix = TRANSCRIPTOMIC_AC16_GLYCO_MITO_VOLCANO$output_prefix,
  feature_col = TRANSCRIPTOMIC_AC16_GLYCO_MITO_VOLCANO$feature_col,
  lfc_col = TRANSCRIPTOMIC_AC16_GLYCO_MITO_VOLCANO$lfc_col,
  padj_col = TRANSCRIPTOMIC_AC16_GLYCO_MITO_VOLCANO$padj_col,
  lfc_cut = TRANSCRIPTOMIC_AC16_GLYCO_MITO_VOLCANO$lfc_cut,
  padj_cut = TRANSCRIPTOMIC_AC16_GLYCO_MITO_VOLCANO$padj_cut,
  title = TRANSCRIPTOMIC_AC16_GLYCO_MITO_VOLCANO$title
)
```

## IPS

### DEG

```{r}
# iPSC transcriptomics pipeline
# This caller keeps project-specific choices in config.R:
# - input paths
# - output paths
# - excluded lines
# - requested DEG comparisons

# 1. Define output folders.
out_dir_ips <- file.path(PATH.IPS_results, "01.Transcriptomic")
deg_dir_ips <- file.path(out_dir_ips, "deg")
dir.create(deg_dir_ips, recursive = TRUE, showWarnings = FALSE)

# 2. Load iPSC sample metadata and exclude line 6132.
meta_filtered <- read_tsv(PATH.TRANSCRIPTOMIC_SAMPLE_METADATA) %>% 
  filter(dataset == TRANSCRIPTOMIC_IPS_DATASET) %>% 
  filter(!line %in% TRANSCRIPTOMIC_IPS_EXCLUDED_LINES)

# 3. Normalize counts and generate QC plots on the filtered iPSC subset.
message("Running normalization for iPSC transcriptomics, excluding line(s): ",
        paste(TRANSCRIPTOMIC_IPS_EXCLUDED_LINES, collapse = ", "))
normalize_and_qc(
  counts_path = PATH.TRANSCRIPTOMIC_RAW_DATA, 
  meta = meta_filtered, 
  dataset = TRANSCRIPTOMIC_IPS_DATASET, 
  out_dir = out_dir_ips
)

# 4. Run all DEG comparisons defined in config.R.
for (i in seq_len(nrow(TRANSCRIPTOMIC_IPS_DEG_COMPARISONS))) {
  comparison <- TRANSCRIPTOMIC_IPS_DEG_COMPARISONS[i, ]

  message("Running DEG comparison: ", comparison$tag,
          " [", comparison$section, "]")

  run_deg(
    counts_path = PATH.TRANSCRIPTOMIC_RAW_DATA, 
    meta = meta_filtered, 
    dataset = TRANSCRIPTOMIC_IPS_DATASET, 
    subset_expr = comparison$subset_expr,
    design = comparison$design,
    contrast = c(
      comparison$contrast_factor,
      comparison$contrast_case,
      comparison$contrast_control
    ),
    tag = comparison$tag, 
    out_dir = deg_dir_ips
  )
}

message("iPSC transcriptomics analysis complete. Results written to: ", out_dir_ips)
```

### Enrichment analysis


```{r}
# iPSC transcriptomics enrichment
# Run Reactome GSEA and g:Profiler enrichment for every iPSC DEG table
# produced by the previous chunk.

ips_enrichment_analysis <- TRANSCRIPTOMIC_ENRICHMENT_ANALYSES %>%
  filter(dataset == TRANSCRIPTOMIC_IPS_DATASET)

stopifnot(nrow(ips_enrichment_analysis) == 1)

message("\nRunning transcriptomics enrichment for: ",
        ips_enrichment_analysis$dataset)

run_enrichment_for_deg_directory(
  deg_dir = ips_enrichment_analysis$deg_dir,
  out_dir = ips_enrichment_analysis$out_dir,
  gene_col = ips_enrichment_analysis$gene_col,
  fc_col = ips_enrichment_analysis$fc_col,
  padj_col = ips_enrichment_analysis$padj_col,
  lfc_cut = ips_enrichment_analysis$lfc_cut,
  padj_cut = ips_enrichment_analysis$padj_cut,
  gene_type = ips_enrichment_analysis$gene_type
)
```

### Mitocarta-specific mapping

```{r}
# iPSC transcriptomics MitoCarta plots
# Generate MitoCarta-specific detailed tables and signed pathway barplots
# from the iPSC transcriptomics DEG tables.

ips_mitocarta_analysis <- TRANSCRIPTOMIC_MITOCARTA_ANALYSES %>%
  filter(dataset == TRANSCRIPTOMIC_IPS_DATASET)

stopifnot(nrow(ips_mitocarta_analysis) == 1)

run_mitocarta_plots_transcriptomics(
  deg_dir = ips_mitocarta_analysis$deg_dir,
  mitocarta_file = ips_mitocarta_analysis$mitocarta_path,
  out_dir = ips_mitocarta_analysis$out_dir,
  dataset = ips_mitocarta_analysis$dataset,
  output_prefix = ips_mitocarta_analysis$output_prefix,
  contrast_keep = NULL,
  lfc_cut = ips_mitocarta_analysis$lfc_cut,
  padj_cut = ips_mitocarta_analysis$padj_cut,
  levels_keep = ips_mitocarta_analysis$levels_keep
)
```

### Glycolysis/mitocarta volcano plot

```{r}
# iPSC transcriptomics volcano restricted to MitoCarta and KEGG/Reactome
# glycolysis genes, with C/T and C/C shown as side-by-side panels.

plot_mitocarta_glycolysis_volcano(
  comparisons = TRANSCRIPTOMIC_IPS_GLYCO_MITO_VOLCANO$comparisons,
  mitocarta_file = PATH.MITOCARTA_DB,
  out_dir = TRANSCRIPTOMIC_IPS_GLYCO_MITO_VOLCANO$out_dir,
  output_prefix = TRANSCRIPTOMIC_IPS_GLYCO_MITO_VOLCANO$output_prefix,
  feature_col = TRANSCRIPTOMIC_IPS_GLYCO_MITO_VOLCANO$feature_col,
  lfc_col = TRANSCRIPTOMIC_IPS_GLYCO_MITO_VOLCANO$lfc_col,
  padj_col = TRANSCRIPTOMIC_IPS_GLYCO_MITO_VOLCANO$padj_col,
  lfc_cut = TRANSCRIPTOMIC_IPS_GLYCO_MITO_VOLCANO$lfc_cut,
  padj_cut = TRANSCRIPTOMIC_IPS_GLYCO_MITO_VOLCANO$padj_cut,
  title = TRANSCRIPTOMIC_IPS_GLYCO_MITO_VOLCANO$title
)
```



# Proteomic

## AC16

### DEP

```{r}
# AC16 proteomics DEP generation
# This reproduces the historical single-batch AC16 DEP workflow:
# raw report -> filtering -> scale normalization -> BPCA imputation -> limma.

run_ac16_proteomics_dep(
  report_file = PROTEOMIC_AC16_ANALYSIS$report_file,
  out_dir = PROTEOMIC_AC16_ANALYSIS$out_dir,
  sample_groups = PROTEOMIC_AC16_ANALYSIS$sample_groups,
  contrast_defs = PROTEOMIC_AC16_ANALYSIS$contrast_defs,
  normalized_matrix_file = PROTEOMIC_AC16_ANALYSIS$normalized_matrix_file,
  min_rep_per_group = PROTEOMIC_AC16_ANALYSIS$min_rep_per_group,
  min_groups_required = PROTEOMIC_AC16_ANALYSIS$min_groups_required,
  nPcs_impute = PROTEOMIC_AC16_ANALYSIS$nPcs_impute,
  lfc_cut = PROTEOMIC_AC16_ANALYSIS$lfc_cut,
  padj_cut = PROTEOMIC_AC16_ANALYSIS$padj_cut
)
```


### QC and volcano plots

```{r}
# AC16 proteomics QC and volcano plots
# QC plots use the normalized no-50.50 matrix produced by the DEP chunk.

ac16_proteomics_meta <- build_ac16_proteomics_metadata(
  PROTEOMIC_AC16_ANALYSIS$sample_groups
)

run_proteomics_matrix_qc_plots(
  matrix_file = PROTEOMIC_AC16_PLOT_ANALYSIS$matrix_file,
  metadata = ac16_proteomics_meta,
  sample_col = "sample",
  color_col = "clone",
  shape_col = "condition",
  label_col = "sample",
  out_dir = PROTEOMIC_AC16_PLOT_ANALYSIS$qc_out_dir,
  dataset_label = PROTEOMIC_AC16_PLOT_ANALYSIS$dataset_label,
  annotation_cols = c("clone", "condition")
)

run_proteomics_volcano_plots(
  dep_dir = PROTEOMIC_AC16_PLOT_ANALYSIS$dep_dir,
  out_dir = PROTEOMIC_AC16_PLOT_ANALYSIS$volcano_out_dir,
  file_pattern = PROTEOMIC_AC16_PLOT_ANALYSIS$file_pattern,
  lfc_cut = PROTEOMIC_AC16_PLOT_ANALYSIS$lfc_cut,
  padj_cut = PROTEOMIC_AC16_PLOT_ANALYSIS$padj_cut
)
```

### Glycolysis/mitocarta volcano plot

```{r}
# AC16 proteomics volcano restricted to MitoCarta and KEGG/Reactome glycolysis
# proteins, with C/T and C/C shown as side-by-side panels.

plot_mitocarta_glycolysis_volcano(
  comparisons = PROTEOMIC_AC16_GLYCO_MITO_VOLCANO$comparisons,
  mitocarta_file = PATH.MITOCARTA_DB,
  out_dir = PROTEOMIC_AC16_GLYCO_MITO_VOLCANO$out_dir,
  output_prefix = PROTEOMIC_AC16_GLYCO_MITO_VOLCANO$output_prefix,
  feature_col = PROTEOMIC_AC16_GLYCO_MITO_VOLCANO$feature_col,
  lfc_col = PROTEOMIC_AC16_GLYCO_MITO_VOLCANO$lfc_col,
  padj_col = PROTEOMIC_AC16_GLYCO_MITO_VOLCANO$padj_col,
  lfc_cut = PROTEOMIC_AC16_GLYCO_MITO_VOLCANO$lfc_cut,
  padj_cut = PROTEOMIC_AC16_GLYCO_MITO_VOLCANO$padj_cut,
  title = PROTEOMIC_AC16_GLYCO_MITO_VOLCANO$title
)
```


### Enrichment analysis

```{r}
# AC16 proteomics enrichment
# Reuse the generic enrichment functions with limma column names.

ac16_proteomics_enrichment <- PROTEOMIC_ENRICHMENT_ANALYSES %>%
  filter(dataset == "AC16")

stopifnot(nrow(ac16_proteomics_enrichment) == 1)

run_enrichment_for_deg_directory(
  deg_dir = ac16_proteomics_enrichment$dep_dir,
  out_dir = ac16_proteomics_enrichment$out_dir,
  gene_col = ac16_proteomics_enrichment$gene_col,
  fc_col = ac16_proteomics_enrichment$fc_col,
  padj_col = ac16_proteomics_enrichment$padj_col,
  lfc_cut = ac16_proteomics_enrichment$lfc_cut,
  padj_cut = ac16_proteomics_enrichment$padj_cut,
  gene_type = ac16_proteomics_enrichment$gene_type,
  file_pattern = ac16_proteomics_enrichment$file_pattern
)
```


## IPS

### DEP

```{r}
# iPSC proteomics preprocessing
# This creates the merged scale-normalized non-imputed matrix used for DEP.
# BPCA-imputed and batch-corrected matrices are written only as QC continuity
# outputs and are not used for the limma inference step below.

run_ips_proteomics_preprocessing(
  report240_file = PROTEOMIC_IPS_PREPROCESSING$report240_file,
  report480_file = PROTEOMIC_IPS_PREPROCESSING$report480_file,
  out_base = PROTEOMIC_IPS_PREPROCESSING$out_base,
  trim_tail_240 = PROTEOMIC_IPS_PREPROCESSING$trim_tail_240,
  trim_tail_480 = PROTEOMIC_IPS_PREPROCESSING$trim_tail_480,
  min_n_per_group = PROTEOMIC_IPS_PREPROCESSING$min_n_per_group,
  nPcs_impute = PROTEOMIC_IPS_PREPROCESSING$nPcs_impute,
  exclude_lines = PROTEOMIC_IPS_PREPROCESSING$exclude_lines
)

# iPSC proteomics DEP generation
# The model uses the normalized non-imputed matrix and includes Batch as a
# covariate, matching the cleaned iPSC inference strategy.

run_ips_proteomics_dep(
  matrix_file = PROTEOMIC_IPS_ANALYSIS$matrix_file,
  metadata_file = PROTEOMIC_IPS_ANALYSIS$metadata_file,
  report_files = PROTEOMIC_IPS_ANALYSIS$report_files,
  out_dir = PROTEOMIC_IPS_ANALYSIS$out_dir,
  condition_levels = PROTEOMIC_IPS_ANALYSIS$condition_levels,
  contrast_defs = PROTEOMIC_IPS_ANALYSIS$contrast_defs,
  exclude_lines = PROTEOMIC_IPS_ANALYSIS$exclude_lines,
  lfc_cut = PROTEOMIC_IPS_ANALYSIS$lfc_cut,
  padj_cut = PROTEOMIC_IPS_ANALYSIS$padj_cut
)
```

### QC and volcano plots

```{r}
# iPSC proteomics QC and volcano plots
# QC plots use the normalized non-imputed matrix; missing values are median
# imputed inside the plotting wrapper for PCA and distance heatmaps only.

ips_proteomics_meta <- read_ips_proteomics_metadata(
  metadata_file = PROTEOMIC_IPS_PLOT_ANALYSIS$metadata_file,
  exclude_lines = PROTEOMIC_IPS_PLOT_ANALYSIS$exclude_lines
)

run_proteomics_matrix_qc_plots(
  matrix_file = PROTEOMIC_IPS_PLOT_ANALYSIS$matrix_file,
  metadata = ips_proteomics_meta,
  sample_col = "sample_uid",
  color_col = "Phenotype",
  shape_col = "Batch",
  label_col = "Sample_ID",
  out_dir = PROTEOMIC_IPS_PLOT_ANALYSIS$qc_out_dir,
  dataset_label = PROTEOMIC_IPS_PLOT_ANALYSIS$dataset_label,
  annotation_cols = c("Batch", "Phenotype")
)

run_proteomics_volcano_plots(
  dep_dir = PROTEOMIC_IPS_PLOT_ANALYSIS$dep_dir,
  out_dir = PROTEOMIC_IPS_PLOT_ANALYSIS$volcano_out_dir,
  file_pattern = PROTEOMIC_IPS_PLOT_ANALYSIS$file_pattern,
  lfc_cut = PROTEOMIC_IPS_PLOT_ANALYSIS$lfc_cut,
  padj_cut = PROTEOMIC_IPS_PLOT_ANALYSIS$padj_cut
)
```

### Glycolysis/mitocarta volcano plot

```{r}
# iPSC proteomics volcano restricted to MitoCarta and KEGG/Reactome glycolysis
# proteins, with C/T and C/C shown as side-by-side panels.

plot_mitocarta_glycolysis_volcano(
  comparisons = PROTEOMIC_IPS_GLYCO_MITO_VOLCANO$comparisons,
  mitocarta_file = PATH.MITOCARTA_DB,
  out_dir = PROTEOMIC_IPS_GLYCO_MITO_VOLCANO$out_dir,
  output_prefix = PROTEOMIC_IPS_GLYCO_MITO_VOLCANO$output_prefix,
  feature_col = PROTEOMIC_IPS_GLYCO_MITO_VOLCANO$feature_col,
  lfc_col = PROTEOMIC_IPS_GLYCO_MITO_VOLCANO$lfc_col,
  padj_col = PROTEOMIC_IPS_GLYCO_MITO_VOLCANO$padj_col,
  lfc_cut = PROTEOMIC_IPS_GLYCO_MITO_VOLCANO$lfc_cut,
  padj_cut = PROTEOMIC_IPS_GLYCO_MITO_VOLCANO$padj_cut,
  title = PROTEOMIC_IPS_GLYCO_MITO_VOLCANO$title
)
```

### Enrichment analysis

```{r}
# iPSC proteomics enrichment
# Reuse the generic enrichment functions with limma column names.

ips_proteomics_enrichment <- PROTEOMIC_ENRICHMENT_ANALYSES %>%
  filter(dataset == "IPS")

stopifnot(nrow(ips_proteomics_enrichment) == 1)

run_enrichment_for_deg_directory(
  deg_dir = ips_proteomics_enrichment$dep_dir,
  out_dir = ips_proteomics_enrichment$out_dir,
  gene_col = ips_proteomics_enrichment$gene_col,
  fc_col = ips_proteomics_enrichment$fc_col,
  padj_col = ips_proteomics_enrichment$padj_col,
  lfc_cut = ips_proteomics_enrichment$lfc_cut,
  padj_cut = ips_proteomics_enrichment$padj_cut,
  gene_type = ips_proteomics_enrichment$gene_type,
  file_pattern = ips_proteomics_enrichment$file_pattern
)
```


# Metabolomic

## AC16

```{r}
# AC16 metabolomics DEM generation and QC plots
# The function keeps the historical cell-type-specific normalization.

res_metabo_ac16 <- run_metabolomics_dem_by_celltype(
  celltype = METABOLOMIC_AC16_ANALYSIS$celltype,
  raw_data_file = METABOLOMIC_AC16_ANALYSIS$raw_data_file,
  out_dir = METABOLOMIC_AC16_ANALYSIS$out_dir,
  target_clones = METABOLOMIC_AC16_ANALYSIS$target_clones,
  outliers = METABOLOMIC_AC16_ANALYSIS$outliers,
  qual_cut = METABOLOMIC_AC16_ANALYSIS$qual_cut,
  lfc_cut = METABOLOMIC_AC16_ANALYSIS$lfc_cut,
  padj_cut = METABOLOMIC_AC16_ANALYSIS$padj_cut,
  make_qc = TRUE,
  make_volcano = TRUE
)
```



## IPS

```{r}
# iPSC metabolomics DEM generation and QC plots
# The retained clones and outlier samples are configured in config.R.

res_metabo_ips <- run_metabolomics_dem_by_celltype(
  celltype = METABOLOMIC_IPS_ANALYSIS$celltype,
  raw_data_file = METABOLOMIC_IPS_ANALYSIS$raw_data_file,
  out_dir = METABOLOMIC_IPS_ANALYSIS$out_dir,
  target_clones = METABOLOMIC_IPS_ANALYSIS$target_clones,
  output_exclude_pattern = METABOLOMIC_IPS_ANALYSIS$output_exclude_pattern,
  outliers = METABOLOMIC_IPS_ANALYSIS$outliers,
  qual_cut = METABOLOMIC_IPS_ANALYSIS$qual_cut,
  lfc_cut = METABOLOMIC_IPS_ANALYSIS$lfc_cut,
  padj_cut = METABOLOMIC_IPS_ANALYSIS$padj_cut,
  make_qc = TRUE,
  make_volcano = TRUE
)
```





# Clustering C/C and C/T

## AC16

### Clustering heatmap

```{r}
# AC16 multi-omics C/T vs C/C stimulation clustering
# This writes the cluster assignment table plus high-resolution heatmap and
# separate shared legends.

ac16_ct_cc_cluster <- run_multiomics_ct_cc_clustering(
  analysis = MULTIOMICS_CLUSTERING_AC16,
  plot_settings = CLUSTERING_PLOT_SETTINGS,
  make_heatmap = TRUE,
  make_composition = FALSE,
  run_ora = FALSE
)
```

### Omic composition

```{r}
# Omic composition per C/T vs C/C response cluster.

plot_multiomics_cluster_composition(
  annot_tbl = ac16_ct_cc_cluster$table,
  out_dir = MULTIOMICS_CLUSTERING_AC16$out_dir,
  output_prefix = MULTIOMICS_CLUSTERING_AC16$output_prefix,
  plot_settings = CLUSTERING_PLOT_SETTINGS,
  dpi = MULTIOMICS_CLUSTERING_AC16$dpi
)
```

### Reactome ORA

```{r}
# Reactome over-representation analysis by cluster.
# The ORA uses transcriptomic and proteomic gene symbols only.

ac16_ct_cc_ora <- run_multiomics_cluster_reactome(
  annot_tbl = ac16_ct_cc_cluster$table,
  out_dir = MULTIOMICS_CLUSTERING_AC16$out_dir,
  output_prefix = MULTIOMICS_CLUSTERING_AC16$output_prefix
)
```

## IPS

### Clustering heatmap

```{r}
# iPSC-CM multi-omics C/T vs C/C stimulation clustering
# This uses the same colors, cluster definitions, and omic scale limits as AC16.

ips_ct_cc_cluster <- run_multiomics_ct_cc_clustering(
  analysis = MULTIOMICS_CLUSTERING_IPS,
  plot_settings = CLUSTERING_PLOT_SETTINGS,
  make_heatmap = TRUE,
  make_composition = FALSE,
  run_ora = FALSE
)
```

### Omic composition

```{r}
# Omic composition per C/T vs C/C response cluster.

plot_multiomics_cluster_composition(
  annot_tbl = ips_ct_cc_cluster$table,
  out_dir = MULTIOMICS_CLUSTERING_IPS$out_dir,
  output_prefix = MULTIOMICS_CLUSTERING_IPS$output_prefix,
  plot_settings = CLUSTERING_PLOT_SETTINGS,
  dpi = MULTIOMICS_CLUSTERING_IPS$dpi
)
```

### Reactome ORA

```{r}
# Reactome over-representation analysis by cluster.
# The ORA uses transcriptomic and proteomic gene symbols only.

ips_ct_cc_ora <- run_multiomics_cluster_reactome(
  annot_tbl = ips_ct_cc_cluster$table,
  out_dir = MULTIOMICS_CLUSTERING_IPS$out_dir,
  output_prefix = MULTIOMICS_CLUSTERING_IPS$output_prefix
)
```

# Public data comparison control


## RNA-seq CCC/CTRL

```{r}
public_rnaseq_ccc_ctrl <- run_public_expression_exploration(
  PUBLIC_RNASEQ_CCC_CTRL_ANALYSIS
)
```

## RNA-seq all phenotypes

```{r}
public_rnaseq_all_phenotypes <- run_public_expression_exploration(
  PUBLIC_RNASEQ_ALL_PHENOTYPES_ANALYSIS
)
```

## Microarray CCC/CTRL

```{r}
public_microarray_ccc_ctrl <- run_public_expression_exploration(
  PUBLIC_MICROARRAY_CCC_CTRL_ANALYSIS
)
```

## Microarray all phenotypes

```{r}
# DCM will be included automatically here when matching microarray files are added.
public_microarray_all_phenotypes <- run_public_expression_exploration(
  PUBLIC_MICROARRAY_ALL_PHENOTYPES_ANALYSIS
)
```
